\documentclass[margin,line]{res}
\usepackage{amsmath, amssymb}
\usepackage{eurosym}
\usepackage{hyperref}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{Ilya Mandel \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{4in}p{2in}}
School of Physics and Astronomy, Monash University \\
19 Rainforest Walk, Clayton,  VIC, 3168, Australia \\
{\it E-mail:}  ilya.mandel@monash.edu \\
{\it WWW:} http://ilyamandel.github.io \\         
\end{tabular}


%\section{\sc Research Interests}
%\begin{tabular}{@{}p{3in}p{3in}}
%Gravitational-Wave Astronomy & Evolution of Massive Binaries \\
%Astrophysics of Compact Objects & Astrostatistics \\  %Gravitational-Wave Data Analysis
%\end{tabular}

\section{\sc Education}
{\bf California Institute of Technology}, Pasadena, CA USA\\
\vspace*{-.1in}
\begin{list1}
\item[] Ph.D. in Physics (conferred June 2008)
\begin{list2}
\vspace*{.05in}
\item Dissertation Title:  ``The Three Ss of Gravitational Wave Astronomy: 
Sources, Signals, Searches'' 
\item Advisor:  Kip S. Thorne
\end{list2}
\vspace*{.05in}
\item[] M.S. in Physics, 2003 
\end{list1}

{\bf Stanford University}, Stanford, CA USA\\
\vspace*{-.1in}
\begin{list1}
\item[] M.S. in Computer Science (Theory specialization), 2001
\vspace*{.05in}
\item[] B.S. in Physics, with Distinction and Departmental Honors, 2000 
\end{list1}


%\section{\sc Work Experience}
\section{\sc Academic Experience}

{\bf Monash University, Australia}\\
{\em Professor of Astrophysics}  \hfill {\bf 2019 - present}

{\bf University of Birmingham, UK}\\
{\em Honorary Professor}  \hfill {\bf 2019 - present}\\
{\em Professor of Theoretical Astrophysics} \hfill {\bf 2016 - 2019}\\
{\em Senior Lecturer} \hfill {\bf 2014 - 2016}\\
{\em Lecturer} \hfill {\bf 2011 - 2014}

{\bf NSF Astronomy \& Astrophysics Postdoctoral Fellow \hfill {2009 - 2011}}\\
At Northwestern 9/2009-6/2010; at MIT 7/2010-8/2011.
 
{\bf Northwestern University}, Evanston, IL USA\\
\vspace*{.02in}
{\em Postdoctoral Scholar in Theoretical Astrophysics  \hfill {\bf 2007 - 2009}}\\
Mentor: Vicky Kalogera
%Research on astrophysical sources of gravitational waves and data-analysis challenges posed by current and planned gravitational-wave detectors

{\bf California Institute of Technology}, Pasadena, CA USA\\
\vspace*{.02in}
{\em Research Assistant} \hfill {\bf 2006 - 2007}\\
\vspace*{0.02in}
 {\em Teaching Assistant} \hfill {\bf 2001 - 2006}
%Teaching recitation sections for sophomore physics (waves, quantum mechanics, statistical mechanics); supervision of classical and modern physics lab courses and computational methods in physics

{\bf Stanford University}, Stanford, CA USA\\
\vspace*{.02in}
{\em Research Assistant, Gravity Probe B} \hfill {\bf 1996 - 2003}\\
%Physics research in the Data Analysis group of GP-B: data-analysis algorithm development, modeling, theoretical investigation of trapped magnetic flux
\vspace*{.02in}
{\em Research and Teaching Assistant, Computer Science} \hfill {\bf 1999}
%Research on the efficiency and feasibility of various routing algorithms in a congested network;  Teaching Assistant for ``Design and Analysis of Algorithms'' course

%{\bf Software Development}, Silicon Valley, CA USA\\ 
%{\em Software developer, Contractor} \hfill {\bf 1999-2002}\\
%Development in Java, including servlets and JSP, SQL, C/C++; algorithm design; software architecture %on contract for several companies, including Kana Communications, Epitrope, and TopCoder, Inc.

\section{\sc Awards} 
Australian Research Council Future Fellow, 2019-2023\\
%Elected Patron of Birmingham AstroSoc student society, 2017\\
Breakthrough Prize in Fundamental Physics (part of LIGO team), May 2016\\
SAMSI (Statistical and Applied Mathematical Science Institute) Research Fellow, 2016--2017\\
College of Engineering and Physical Sciences paper of the month award, February 2016\\
Classical and Quantum Gravity highlights -- most cited article in 2 years (``Predictions for the rates of compact binary coalescences observable by ground-based gravitational-wave detectors''), 2012\\
Head of School commendation letters for excellence in teaching (multiple years, 2013--2018)\\
Kevin Westfold Distinguished Visitor, Monash Center for Astrophysics, 2014\\
%NSF Astronomy and Astrophysics Postdoctoral Fellowship\\
%Dean's Award for Academic Achievement (excellence in research), Stanford University\\
%Tau Beta Pi (engineering honor society) Member\\
%National Merit Scholar, National Advanced Placement Scholar\\
%Robert Byrd Scholarship Recipient\\


\section{\sc Service}

%{\it International/national leadership:}\\
Aspen Center for Physics board member (2016 -- current)\\
Gravitational-Wave International Committee 3G Science Case team member, Binaries working group co-chair (2017 -- 2019)\\
Organising Committee Member, IAU Binary and Multiple Star Systems Commission (2018 -- present)\\
Chair, steering committee of the Australian National Institute for Theoretical Astrophysics (ANITA; 2020 -- current [deputy chair, 2019-2020])\\
Councillor, Astronomical Society of Australia (2019 -- 2021)\\
Council member, International Astrostatistics Association (2021 -- 2023)\\
%{\it Journal editing and review, grant review:}\\
Scientific Editor, Astrophysical Journal\\
Editorial Board member, Nature Scientific Data\\
%Reviewer for the Astrophysical Journal, Physical Review, Classical and Quantum Gravity, Monthly Notices of the Royal Astronomical Society, Philosophical Transactions of the Royal Society, Nature journals, Science (2008--current); Institute of Physics Trusted Reviewer (2020) \\
%Grant reviewer for NASA (USA; including as member of NASA Astrophysics Theory Grant Panel), NSF (USA), Hungarian Scientific Research Fund, STFC (UK), NWO (Netherlands Organisation for Scientific Research), European Research Council, CONICYT (Chile), ARC (Australia), CRC (Canada) (2008--current)\\
%{\it Collaboration leadership/membership:}\\
%LIGO Scientific Collaboration member (2005--2016), LSC Council member (2012 -- 2016)\\
%LSC internal reviewer (2009 -- 2016), intermediate mass black hole source group co-chair (2012 -- 2016)\\
%LISA Consortium Member\\
%Mock LISA Data Challenge and Parameter Estimation Taskforce member\\
%Einstein Telescope Science Working Group member\\
%LOFT science team member\\
%Member of several electromagnetic transient surveys (e.g., ePESSTO) and multi-messenger  consortia for following up gravitational-wave signals (e.g., ENGRAVE, where I co-chair the Populations theory group)\\
Organised 20+ international conferences, meetings, workshops and schools\\
Chief Investigator, Australian Research Council Centre of Excellence for Gravitational Wave Discovery (OzGrav)\\
%{\it Meeting organisation:}\\
%SOC member, inaugural South African GW workshop (2011)\\
%Convener of relativistic astrophysics session, GR-20 (2013)\\
%Co-organizer and SOC co-chair, ``Science with the first gravitational-wave detections'' (2013)\\
%Lead organizer, Aspen Physics Center Workshop on Ultra-compact Binaries as Laboratories for Fundamental Physics (2014)\\
%Main organizer and SOC chair, Gravitational-wave Astrophysics meeting at COSPAR (2014)\\
%Program Leader, SAMSI Program on Statistical, Mathematical and Computational Methods for Astronomy (2016-2017)\\
%Main organizer and SOC chair, Massive Binary Evolution meeting at COSPAR (2016 [cancelled because of current events in Turkey])\\
%International Society on General Relativity \& Gravitation, Nominating Committee member (2016 -- current)\\
%Organizer, SAMSI workshop on Astrophysical Population Emulation and Uncertainty Quantification (2017)\\
%SOC member, Alpine Cosmology Workshop (2017 -- current)\\
%Co-director, Kavli Summer Program in Astrophysics 2017: Astrophysics with gravitational wave detections (2017)\\
%Co-organizer and SOC co-chair, Lorentz Center Workshop ``And then there was light:  Electromagnetic signatures of stellar mass binary black hole mergers'' (2017)\\
%Co-organizer, Munich Institute for Astro- and Particle Physics program ``Precision gravity: from the LHC to LISA'' (2019)\\
%SOC Member, EAS Symposium ``What have we learned from the observed population of gravitational wave sources?'' (2020)\\
%SOC Member, COSPAR event ``X- and Gamma-ray Counterparts of New Transients in the Multimessenger Era'' (2020/2021)\\
%Astronomical Society of Australia 2020 (virtual) science meeting organiser\\
%ANITA 2021 workshop (virtual) lead organiser\\
%SOC co-chair, EAS session ``Where are the BH-NS binaries?'' (2021)\\
%SOC member, GWPAW 2021\\
%SOC member, Nuclear burning in massive stars: towards the formation of binary black holes (2021)\\

%{\it Institutional contributions:}\\
%University of Birmingham astrophysics seminar organizer (2012--2015)\\
%University of Birmingham physics and astronomy colloquium organizer (2015--current)\\
%University of Birmingham head of graduate admissions for astronomy (2012 -- current)\\
%University of Birmingham Faculty Senate representative elected for Engineering and Physical Sciences (2016 -- current)\\
%School and College Equality and Diversity Committee member, University of Birmingham (2014 -- 2017) \\
%Monash University astrophysics seminar and school colloquium co-organiser (2019)\\


\section{\sc Supervision}
7 Postdoctoral associates (3 are now tenured or tenure-track faculty)\\
18 PhD students (13 have completed PhDs, including 3 who are now tenured or tenure-track faculty)\\
40 undergraduate, honours, and masters students\\


\section{\sc Recent Grants}
\begin{tabular}{@{}p{0.8in}p{4.7in}}
2019--2024 & Australian Research Council Future Fellowship (PI): {\it  Shining gravitational waves on binary astrophysics} [AUD \$936k from ARC, AUD \$996k in matching Monash funds]\\
2017--2020 & NERC grant (Co-I): {\it Reducing Greenhouse Climate Proxy Uncertainty} [total value of grant \pounds 434k]\\
2016--2019 & STFC Consolidated grant (Co-I): {\it Searching for intermediate mass ratio coalescences in Advanced LIGO/Virgo data} [total value of grant \pounds1,834k]\\
\end{tabular}
%Co-I, STFC grant \it{Supporting UK Involvement in the Operation of Advanced LIGO}, 2016--2019\\
%PI, RAS Bursary \it{Studying black holes with gravitational waves}, 2015\\
%Monash University grant for sabbatical visit (Kevin Westfold Distinguished Visitor), 2015\\
%South African National Institute of Theoretical Physics (NITheP) long-term visitor grant, 2014\\
%Co-I, Marie Curie Initial Training Network grant {\it GraWIToN}, 2013--2017\\
%PI, Leverhulme Trust grant, \it{Testing general relativity with ground-based gravitational-wave observations}, 2013--2016\\
%Co-I, STFC consolidated grant {\it Gravitational wave observations of compact binary systems},2013--2016\\
%Co-I, ASPERA grant, {\it Networking and R\&D for the Einstein Telescope}, 2013--2016\\%total amount to Bham -- 59K, including 0.35 months of my salary
%PI on NSF Astronomy and Astrophysics Postdoctoral Fellowship grant ``Gravitational-wave astronomy: a new window on the universe''\\ %[total grant amount over 3 years: \$249,000]\\
%Co-I on NASA ATP grant ``Binary White Dwarfs: Gravitational Wave Astrophysics and Data Analysis''\\


\section{\sc Sample of recent presentations (since 2018)}

Seminars and colloquia at: University of California, Berkeley, University of California, Santa Cruz, St Petersburg Academic University, Melbourne University, University of Western Australia, Macquarie University, TIFR (Mumbai, India), University of California, Los Angeles, National Institute of Theoretical Physics, South Africa, Hebrew University of Jerusalem.\\
Invited talks at ``UQ for inverse problems in complex systems'', Isaac Newton Institute, Cambridge; Sackler conference on Gravitational-wave Astrophysics, CfA/Harvard; ULX meeting, ISSI, Bonn; Max-Planck meeting at Schloss Ringberg, Germany; Gravitational Wave Astrophysics Conference, Hefei, China; Aspen Centre of Physics; International Statistical Institute World Congress, Kuala-Lumpur, Malaysia\\
Plenary talk, IAU General Assembly, Vienna\\
Opening plenary talk, Amaldi conference on ``Accelerating gravitational wave science''\\
Les Houches lecture series on astrophysical sources of gravitational waves\\
Lecture at STFC summer school, Belfast\\

\section{\sc Sample of recent outreach activities (since 2020)}


Co-author (with Leslie Atkins Elliot) of Cosmos Magazine article ``Teaching Physics to Monks''\\
Wrote article ``Gravitational waves: astronomers spot a black hole so massive they weren't sure it could exist'' for The Conversation (in top 5 most read Conversation articles of the month)\\
Co-wrote article ``21 times the SunÕs mass: heaviest stellar black hole in the Milky Way is more massive than we thought'' for The Conversation\\
Lecture at Mornington Peninsula Astronomical Society\\
Australian Institute of Physics Victoria Nobel Lecture\\
Public lecture for the Astronomical Society of Victoria


\newpage

\section{\sc Relevant publications in Refereed Journals since 2017}

\begin{enumerate}

\item G.~P.~Lamb, D.~A.~Kann, J.~J.~Fernandez, I.~Mandel, A.~J.~Levan, N.~R.~Tanvir. 2021. GRB jet structure and the jet break. MNRAS, accepted.  arXiv:2104.11099

\item R.~Smith, S.~Borhanian, B.~Sathyaprakash, F.~Hernandez Vivanco, S.~Field, P.~Lasky, I.~Mandel, S.~Morisaki, D.~Ottaway, B.~Slagmolen, E.~Thrane, D.~T\"{o}yr\"{a}, S.~Vitale.  2021.  Bayesian inference for gravitational waves from binary neutron star mergers in third-generation observatories.  Phys.~Rev.~Letters, accepted. arXiv:2103.12274

\item E.~Grishin, A.~Bobrick, R.~Hirai, I.~Mandel, H.~Perets. 2021.  Supernova explosions in active galactic nuclei discs.  MNRAS, accepted.  arXiv:2105.09953

\item L.~Lin, D.~Bingham, F.~Broekgaarden, I.~Mandel. 2021. Uncertainty quantification of a computer model for binary black hole formation. Annals of Applied Statistics, accepted.  arXiv:2106.01552 

\item J.~Riley, I.~Mandel, P.~Marchant, E.~Butler, K.~Nathaniel, C.~Neijssel, S.~Shortt, A.~Vigna-Gomez.  2021. Chemically Homogeneous Evolution: A rapid population synthesis approach. MNRAS 505, 663.  arXiv:2010.00002

\item J.~C.~A.~Miller-Jones, A.~Bahramian, J.~A.~Orosz, I.~Mandel, L.~Gou, T.~J.~Maccarone, C.~J.~Neijssel et al.  2021.  Cygnus X-1 contains a 21-solar mass black hole -- implications for massive star winds.  Science 371, 1046. arXiv:2102.09091

\item C.~J.~Neijssel, S.~Vinciguerra, A.~Vigna-Gomez, R.~Hirai, J.~C.~A.~Miller-Jones, A.~Bahramian, T.~J.~Maccarone, I.~Mandel.  2021.  Wind mass-loss rates of stripped stars inferred from Cygnus X-1. ApJ 908, 118.  arXiv:2102.09092

\item E.~M.~Rossi, N.~C. Stone, J.~A.~P.~Law-Smith, M.~MacLeod, G.~Lodato, J.~L.~Dai, I.~Mandel.  2021.  The Process of Stellar Tidal Disruption by Supermassive Black Holes. The first pericenter passage.  Space Science Reviews 217, 40.  arXiv:2005.12528

\item D.~Psaltis, C.~Talbot, E.~Payne, I.~Mandel.  2021. Probing the black hole metric. I. Black hole shadows and binary black-hole inspirals.  Phys Rev D, accepted. arXiv:2012.02117

\item A.~Miglio et al. 2020. Age dissection of the Milky Way discs: red giants in the Kepler field.  A\&A, accepted.  arXiv:2004.14806

\item I.~Mandel, B.~M\"{u}ller, J.~Riley, S.~E.~de Mink, A.~Vigna-Gomez, D.~Chattopadhyay. 2021.  Binary population synthesis with probabilistic remnant mass and kick prescriptions. MNRAS 500, 1380.   arXiv:2007.03890

\item L.~du Buisson, P.~Marchant, P.~Podsiadlowski, C.~Kobayashi, F.~B.~Abdalla, P.~Taylor, I.~Mandel, S.~E.~de Mink, T.~J.~Moriya, N.~Langer.  2020. Cosmic Rates of Black Hole Mergers and Pair-Instability Supernovae from Chemically Homogeneous Binary Evolution. MNRAS, 499, 5941.  arXiv:2002.11630

\item I.~Mandel and B.~M\"{u}ller. 2020. Simple recipes for compact remnant masses and natal kicks.  MNRAS 499, 3214.  arXiv:2006.08360

\item K.~Ackley et al. 2020. Neutron Star Extreme Matter Observatory: A kilohertz-band gravitational-wave detector in the global network. PASA, accepted.  arXiv:2007.03128 

\item R.~Hirai, T.~Sato, P.~Podsiadlowski, A.~Vigna-Gomez, I.~Mandel. 2020. Formation pathway for lonely stripped-envelope supernova progenitors: implications for Cassiopeia A.  MNRAS 499, 1154. arXiv:2008.05076

\item A.~Murguia-Berthier, A.~Batta, A.~Janiuk, E.~Ramirez-Ruiz, I.~Mandel, S.~C.~Noble, R.~W.~Everson.  2020.  On the maximum stellar rotation to form a black hole without an accompanying luminous transient.  ApJ Letters 901, L24.  arXiv:2005.10212

\item M.~Nicholl et al. 2020. An outflow powers the optical rise of the nearby, fast-evolving tidal disruption event AT2019qiz. MNRAS 499, 482.  arXiv:2006.02454

\item K.~Ackley et al. 2020. Observational constraints on the optical and near-infrared emission from the neutron starÐblack hole binary merger S190814bv.  Astronomy \& Astrophysics 643, A113.
arXiv:2002.01950

\item A.~Vigna-Gomez, M.~MacLeod, C.~J.~Neijssel, F.~S.~Broekgaarden, S.~Justham, G.~Howitt, S.~E.~de Mink and I.~Mandel.  2020. Common-Envelope Episodes that lead to Double Neutron Star formation.  PASA 37, e038.  arXiv:2001.09829 

\item S.~Vinciguerra, C.~J.~Neijssel, A.~Vigna-G\'{o}mez, I.~Mandel, P.~Podsiadlowski, T.~J.~Maccarone, M.~Nicholl, S.~Kingdon, A.~Perry, F.~Salemi.  2020. Be X-ray binaries in the SMC as (I) indicators of mass transfer efficiency.  MNRAS 498, 4705.  arXiv:2003.00195

\item V.~Korol, I.~Mandel, M.~C.~Miller, R.~P.~Church, M.~B.~Davies. 2020. Merger rates in primordial black hole clusters without initial binaries. MNRAS 496, 994.  arXiv:1911.03483

\item S.~De, M.~MacLeod, R.~W.~Everson, A.~Antoni, I.~Mandel, E.~Ramirez-Ruiz.  2020.  Common Envelope Wind Tunnel: The Effects of Binary Mass Ratio and Implications for the Accretion-Driven Growth of LIGO Binary Black Holes.  ApJ 897, 130.  arXiv:1910.13333

\item S.~L.~Schroeder, M.~MacLeod, A.~Loeb, A.~Vigna-Gomez, I.~Mandel.  2020. Explosions Driven by the Coalescence of a Compact Object with the Core of a Massive-Star Companion Inside a Common Envelope: Circumstellar Properties, Light Curves, and Population Statistics.  ApJ 892, 13.  arXiv:1906.04189

\item I.~Mandel, T.~Fragos. 2020. An alternative interpretation of GW190412 as a binary black hole merger with a rapidly spinning secondary.  ApJ Letters 895, L28. arXiv:2004.09288

\item S.~S.~Bavera, T.~Fragos, Y.~Qin, E.~Zapartas, C.~J.~Neijssel, I.~Mandel, A.~Batta, S.~M.~Gaebel, C.~Kimball, S.~Stevenson.  2020.  The origin of spin in binary black holes: Predicting the distributions of the main observables of Advanced LIGO.  Astronomy \& Astrophysics 635, A97.  arXiv:1906.12257

\item M.~Y.~M.~Lau, I.~Mandel, A.~Vigna-G\'{o}mez, C.~J.~Neijssel, S.~Stevenson, A.~Sesana.  2020.  Detecting Double Neutron Stars with LISA.  MNRAS 492, 3061.  arXiv:1910.12422

\item G.~Howitt, S.~Stevenson, A.~Vigna-Gomez, S.~Justham, N.~Ivanova, T.~E.~Woods, C.~J.~Neijssel, I.~Mandel.  2020.  Luminous Red Novae: population models and future prospects.  MNRAS 492, 3229.  arXiv:1912.07771 

\item P.~Marchant, K.~Breivik, C.~P.~L.~Berry, I.~Mandel, S.~L.~Larson. 2020.  Eclipses of continuous gravitational waves as a probe of stellar structure.  Physical Review D 101, 024039.
arXiv: 1912.04268

\item L.~Wyrzykowski, I.~Mandel.  2020.  Constraining the masses of microlensing black holes and the mass gap with Gaia DR2.  Astronomy \& Astrophysics 636, A20.  arXiv:1904.07789

\item O.~R.~McBrien et al. 2019. SN2018kzr: a rapidly declining transient from the destruction of a white dwarf. ApJ Letters 885, L23.  arXiv:1909.04545

\item G.~Leloudas et al.  2019. The spectral evolution of AT 2018dyb and the presence of metal lines in tidal disruption events.  ApJ 887, 218.  arXiv:1903.03120

\item C.~J.~Neijssel, A.~Vigna-Gomez, S.~Stevenson, J.~W.~Barrett, S.~M.~Gaebel, F.~Broekgaarden, S.~E.~de Mink, D.~Szecsi, S.~Vinciguerra, I.~Mandel.  2019. The effect of the metallicity-specific star formation history on double compact object mergers.  MNRAS 490, 3740.  arXiv:1906.08136

\item F.~S.~Broekgaarden, S.~Justham, S.~E.~de Mink, J.~Gair, I.~Mandel, S.~Stevenson, J.~W.~Barrett, A.~Vigna-Gomez, C.~J.~Neijssel.  2019. STROOPWAFEL: Simulating rare outcomes from astrophysical populations, with application to gravitational-wave sources.  MNRAS 490, 5228.  arXiv:1905.00910

\item R.~X.~Adhikari, P.~Ajith, Y.~Chen, J.~A.~Clark, V.~Dergachev, N.~V.~Fotopoulos, S.~E.~Gossan, I.~Mandel, M.~Okounkova, V.~Raymond, J.~S.~Read.  2019. Astrophysical science metrics for next-generation gravitational-wave detectors.  CQG 36, 245010.  arXiv:1905.02842

\item J.~J.~Andrews, I.~Mandel. 2019. Double Neutron Star Populations and Formation Channels.   2019.  ApJ Letters 880, L8.  arXiv:1904.12745

\item J.~Powell, S.~Stevenson, I.~Mandel, P.~Tino.  2019.  Unmodelled Clustering Methods for Gravitational Wave Populations of Compact Binary Mergers.  MNRAS 488, 3810. arXiv:1905.04825

\item S.~Stevenson, M.~Sampson, J.~Powell, A.~Vigna-G\'{o}mez, C.~J.~Neijssel, D.~Sz\'{e}csi, I.~Mandel.  2019. The impact of pair-instability mass loss on the binary black hole mass distribution.   ApJ 882, 121.  arXiv:1904.02821 

\item A.~Vigna-Gomez, S.~Justham, I.~Mandel, S.~E.~de Mink, P.~Podsiadlowski.  2019.  Massive Stellar Mergers as Precursors of Hydrogen-rich Pulsational Pair Instability Supernovae.  ApJ Letters 876, L29. arXiv:1903.02135

\item I.~Mandel, W.~M.~Farr, J.~R.~Gair.  2019. Extracting distribution parameters from multiple uncertain observations with selection biases.  MNRAS 486, 1086.  arXiv:1809.02063

\item G.~P.~Lamb et al. 2019. The optical afterglow of GW170817 at one year post-merger.  ApJ Letters 870, L15. arXiv:1811.11491

\item S.~Vinciguerra, M.~Branchesi, R.~Ciolfi, I.~Mandel, C.~Neijssel, G.~Stratta.  2019. saprEMo: a simplified algorithm for predicting detections of electromagnetic transients in surveys.  MNRAS 484, 332.  arXiv:1809.08641

\item G.~P.~Lamb, I.~Mandel, L.~Resmi.  2018.  Late-time Evolution of Afterglows from Off-Axis Neutron-Star Mergers.  MNRAS 481, 2581.  arXiv:1806.03843

\item A.~Vigna-G\'{o}mez, C.-J.~Neijssel, S.~Stevenson, J.~W.~Barrett, K.~Belczynski, S.~Justham, S.E.~de Mink, B.~M{\"u}ller, P.~Podsiadlowski, M.~Renzo, D.~Sz{\'e}csi, I.~Mandel.  2018. On the formation history of Galactic double neutron stars.  MNRAS 481, 4009. arXiv:1805.07974

\item W.~M.~Farr, I.~Mandel.  2018.  Comment on ``An excess of massive stars in the local 30 Doradus starburst''.  Science 361, 6400.  arXiv:1807.09772

\item J.~D.~Lyman, G.~P.~Lamb, A.~J.~Levan, I.~Mandel, N.~R.~Tanvir et al.  2018. The optical afterglow of the short gamma-ray burst associated with GW170817.  Nature Astronomy. arXiv:1801.02669

\item J.~W. Barrett, S.~M.~Gaebel, C.~J.~Neijssel, A.~Vigna-G\'{o}mez, S.~Stevenson, C.~P.~L.~Berry, W.~M.~Farr, I.~Mandel.  2018.  Accuracy of inference on the physics of binary evolution from gravitational-wave observations.   MNRAS 477, 4685.  arXiv:1711.06287

\item M.~Cantiello et al. 2018.  A precise distance to the host galaxy of the binary neutron star merger GW170817 using surface brightness fluctuations.  ApJL 854, L31.  arXiv:1801.06080

\item I.~Mandel.  2018. The orbit of GW170817 was inclined by less than 28 degrees to the line of sight.  ApJL 853, L1. arXiv:1712.03958

\item I.~Mandel, A.~Sesana, A.~Vecchio. 2018.  The astrophysical science case for a decihertz gravitational-wave detector.  Classical and Quantum Gravity 35, 054004. arXiv:1710.11187

\item N.~R.~Tanvir, A.~J.~Levan, C.~Gonzalez-Fernandez, O.~Korobkin, I.~Mandel et al. 2017.  The Emergence of a Lanthanide-rich Kilonova Following the Merger of Two Neutron Stars.  ApJL 848, L27.  arXiv:1710.05455 

\item A.~J.~Levan, J.~D.~Lyman, N.~R.~Tanvir, J.~Hjorth, I.~Mandel et al. 2017. The environment of the binary neutron star merger GW170817.  ApJL 848, L28.  arXiv:1710.05444

\item J.~Hjorth et al. 2017. The Distance to NGC 4993: The Host Galaxy of the Gravitational-wave Event GW170817.  ApJL 848, L31.  arXiv:1710.05866

\item B.~P.~Abbott et al. 2017.   A gravitational-wave standard siren measurement of the Hubble constant.  Nature 551, 85. arXiv:1710.05835

\item B.~P.~Abbott et al. 2017. Multi-messenger observations of a binary neutron star merger. ApJL 848, L12. arXiv:1710.05833

\item I.~Mandel, A.~Farmer.  2017. Gravitational waves: Stellar palaeontology.  Nature 547, 284

\item W.~M.~Farr, S.~Stevenson, M.~C.~Miller, I.~Mandel, B.~Farr, A.~Vecchio.  Distinguishing Spin-Aligned and Isotropic Black Hole Populations With Gravitational Waves. 2017. Nature, 548, 426. arXiv:1706.01385

\item P.~Marchant, N.~Langer, P.~Podsiadlowski, T.~Tauris, S.~de Mink, I.~Mandel, T.~Moriya.  2017.  Ultra-luminous X-ray sources and neutron-star-black-hole mergers from very massive close binaries at low metallicity.  A\&A 604, A55.  arXiv:1705.04734

\item S.~Stevenson, A.~Vigna-G\'omez, I.~Mandel, J.~W.~Barrett, C.~J.~Neijssel, D.~Perkins, S.~E.~de Mink.  2017.  Forming GW151226 and LVT151012 through isolated binary evolution.  Nature Communications, 8,  14906.  arXiv:1704.01352

\item S.~Stevenson, C.~P.~L.~Berry, I.~Mandel.  2017.  Hierarchical analysis of gravitational-wave measurements of binary black hole spin-orbit misalignments.  MNRAS 471, 2801. arXiv:1703.06873

\item B.~Bradnick, I.~Mandel, Y.~Levin. 2017.  Stellar binaries in galactic nuclei: tidally stimulated mergers followed by tidal disruptions.  MNRAS 469, 2042.  arXiv:1703.05796

\item S.~Vinciguerra, J.~Veitch, I.~Mandel.  2017.  Accelerating gravitational wave parameter estimation with multi-band template interpolation.  CQG, 34, 115006.  arXiv:1703.02062

\item I.~Mandel, W.~M.~Farr, A.~Colonna, S.~Stevenson, P.~Ti\v{n}o, J.~Veitch.  2017.  Model-independent inference on compact-binary observations.  MNRAS 465, 3254.  arXiv:1608.08223

\end{enumerate}

\section{\sc Recently submitted pre-prints}

\begin{enumerate}

\item R.~Hirai, I.~Mandel. 2021. Observable black hole high-mass X-ray binaries must have $>80\%$ Roche lobe filling companions. arXiv:2108.03774 

\item I.~Mandel, F.~S.~Broekgaarden. 2021. Rates of compact binary coalescences. arXiv:2107.14239

\item A.~Vigna-Gomez, M.~Wassink, J.~Klencki, A.~Istrate, G.~Nelemans, I.~Mandel.  2021. Stellar response after stripping as a model for common-envelope outcomes. arXiv:2107.14526

\item S.~L.~Schr{\o}der, M.~MacLeod, E.~Ramirez-Ruiz, I.~Mandel, T.~Fragos, A.~Loeb, R.~W.~Everson. 2021. The Evolution of Binaries under the Influence of Radiation-Driven Winds
  from a Stellar Companion.  arXiv:2107.09675

\item R.~Willcox, I.~Mandel, E.~Thrane, A.~Deller, S.~Stevenson, A.~Vigna-G{\'o}mez.  2021. Constraints on Weak Supernova Kicks from Observed Pulsar Velocities.  arXiv:2107.04251 

\item F.~S.~Broekgaarden, E.~Berger, C.~J.~Neijssel, A.~Vigna-Gomez, D.~Chattopadhyay, S.~Stevenson, M.~Chruslinska, S.~Justham, S.~E.~de~Mink, I.~Mandel. 2021. The Impact of Massive Binary Star and Cosmic Evolution on Gravitational Wave Observations I: Black Hole - Neutron Star Mergers.  arXiv:2103.02608

\end{enumerate}

\end{resume}
\end{document}




